\documentclass[12pt]{extarticle}

\usepackage{extsizes}
\usepackage{booktabs}
\usepackage{setspace}
\setstretch{1.5}
\setlength{\fboxrule}{2pt}
\usepackage[a4paper, margin=35mm]{geometry}

\begin{document}

\section*{Assignment 3: Interview with Senior Scientist}

\vspace{5mm}
\begin{center}
    \framebox[\textwidth][s]{\hspace{2mm} Author of Assignment: Jane Coates \hspace{5mm} Date: 24/4/2015 \hspace{2mm} } \par
\end{center}
\vspace{5mm}

\textbf{Questions for Interview}

\begin{itemize}
	\item How much time do you need to write the paper?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item Less than a week if storyline, figures and tables are ready. Otherwise, about a month if analysis still needs to be done.
        \end{itemize}
	\item Where do your start (section, pictures, …)?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item Start with the data and see what are the take away messages to be communicated in the paper. All figures and tables are then catered to communicate these messages. Basically, the conclusion is written first and then work backwards with introduction typically the final part written.
        \end{itemize}
	\item When and how do you choose the journal?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item After analysing the data and deciding on which figures and tables are included, the estimated length of the paper is clearer and then the journal is chosen. The choice of journal is also influenced by the maximum paper length defined by the journals.
        \end{itemize}
	\item Do you separate results and discussion?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item Not usually.
        \end{itemize}
	\item How do you structure results and discussion?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item Results that build on each other are present sequentially. Generally the more basic results are presented first then leading up to more complex or downstream implications.
        \end{itemize}
	\item Do you write summary in the end of introduction?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item Not usually unless it is to specify what the paper focuses on and what is not part of the scope of the paper.
        \end{itemize}
	\item How do you identify the authors?
        \begin{itemize}
          \renewcommand\labelitemii{$\rightarrow$}
          \item Anyone who has contributed to the process; e.g. provided data, support for the project, develop the concept, analysis.
        \end{itemize}
\end{itemize}

\end{document}
